---
title: "Logistic Code that does not work"
author: "Michel Ruiz-Fuentes"
format: pdf
editor: visual
date: "`r Sys.Date()`"
---

# \*\*PROF. DUTT :

I do not have a `Choice` variable so I cannot run these code. If I should create a `Choice` variable using the z-score pointers you gave me how would I do this?

```{r, warning=F, message=F}
# # Fit a logistic regression model to predict choice (0 = A, 1 = B) based on Hpa
# Hpa_model <- glm(Choice ~ pHa, data = choices_df, family = binomial())
# # Print the model summary
# summary(Hpa_model)
```

```{r, warning=F, message=F}
# # Fit a logistic regression model to predict choice (0 = A, 1 = B) based on Hpb
# Hpb_model <- glm(Choice ~ pHb, data = choices_df, family = binomial())
# # Print the model summary
# summary(Hpb_model)
```

### [**Probability Density Plot:**]{.underline} 

If you use logistic regression to assess the impact of various independent variables on the likelihood of choosing Gamble A or B, a probability density plot could be a useful visualization to display the distribution of predicted probabilities for each choice. This could help to illustrate any differences in the distribution of predicted probabilities between the two choices.

```{r, warning=F, message=F}
# Assuming you  ave a logistic regression model "logit_model" predicting the binary outcome variable "choice"
# # Extract the predicted probabilities for each choice
# probs <- predict(logit_model, type = "response")
# 
# # Create a density plot for each choice
# ggplot(data.frame(probs = probs, choice = choice), aes(x = probs, fill = choice)) +
#   geom_density(alpha = 0.5) +
#   scale_fill_manual(values = c("#F8766D", "#00BFC4"), name = "Choice") +
# #   xlab("Predicted probability") +
# #   ylab("Density") +
#   ggtitle("Distribution of predicted probabilities for each choice")
```

### [**Heat Map:**]{.underline}

```{r, warning=F, message=F}
# Assuming you have a data frame "df" with two categorical variables "feedback" and "choice"
# Use the "table" function to create a contingency table of frequencies
# freq_table <- table(df$feedback, df$choice)
# 
# # Create a heat map using the "ggplot2" package
# ggplot(data.frame(freq_table), aes(x = Var1, y = Var2, fill = Freq)) +
#   geom_tile() +
#   scale_fill_gradient(low = "#FFFFFF", high = "#0072B2") +
#   xlab("Feedback") +
#   ylab("Choice") +
#   ggtitle("Heat map of frequencies by feedback and choice")
```

# 
